---
title: "Weight of Fish"
author: "Gracie Telles"
date: "Fall 2023`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
library(dplyr)
library(leaps)
Fish = read_csv("Fish.csv")
```

# Predicting Fish Weight

Find the best model using two variables to predict perch weight, and compare this to the best overall model.

## Perch

```{r}
Perch = filter(Fish, Species =='Perch')

```

### Best Models

```{r}
modelPerch = regsubsets(Weight ~ Length1 + Length2 + Length3 + Height + Width, data = Perch)
summary(modelPerch)
```

##The best two variable predictors for Perch weight is by using heigth and width data sets.

```{r}
best2Perch = lm(Weight ~ Height + Width, data = Perch)
summary(best2Perch)
```

### Best Two regressor model

Is Weight = -536 + 74.77*Height + 69.62*Width




## Pike


```{r}
Pike = filter(Fish, Species =='Pike')
```

### Best Models

```{r}
modelPike = regsubsets(Weight ~ Length1 + Length2 + Length3 + Height + Width, data = Pike)
summary(modelPike)
```

##The best 2 variable predictors are Length1 and Length3 data sets.


```{r}
best2Pike = lm(Weight ~ Length1+ Length3, data = Pike)
summary(best2Pike)
```

### Best Two regressor model
Is Weight = -1675.79 + -105.64*Length1 + 141.25*Length3


## Roach

```{r}
Roach = filter(Fish, Species =='Roach')

```

### Best Models

```{r}
modelRoach = regsubsets(Weight ~ Length1 + Length2 + Length3 + Height + Width, data = Roach)
summary(modelRoach)
```

##The best 2 variable predictors are Length3 and Width data sets.

### Best Two regressor model

```{r}
best2Roach = lm(Weight ~ Length3+ Width, data = Roach)
summary(best2Roach)
```

### Best Two regressor model
Is Weight = -319.118 + 8.278*Length3 + 72.300*Width


## Final Summary Statements

The best 2 predictors for Perch weight were Heigth and Width.
The best 2 predictors for Pike weight were Length1 and Length3.
The best 2 predictors for Roach weight were Length3 and Width.